---
title: "Quantitative Methods in Financial Economics"
subtitle: "A glossaRy of recipes in R"
date: "`r format(Sys.time(), '%d %B %Y')`"
author: "Mike Aguilar"
output: 
  html_document:
    mode: selfcontained
    toc: true
    toc_float: true
    number_sections: yes
    toc_depth: 3
---

```{css, echo=FALSE}
.scroll-200 {
  max-height: 200px;
  overflow-y: auto;
  background-color: inherit;
}
```

```{r global-options, include=TRUE, echo = FALSE}
knitr::opts_chunk$set(fig.width=10, fig.height=4,echo=TRUE, warning=FALSE, message=FALSE, class.output="scroll-200")
```


# Purpose {-}
This glossary provides a quick reference guide to key functionality in R for anyone working with macro/financial data.  This glossary is NOT a substitute for a textbook nor is it a substitute for package documentation.  

The glossary is organized into 4 chapters, motivated by the manner in which a quantitative analyst might approach the investing process. 

Chapter 1: Explore --- loading/cleaning financial time series data, EDA

Chapter 2: Explain --- modeling with regressions and similar tools

Chapter 3: Forecast --- general forecasting techniques with examples for returns

Chapter 4: Protect --- portfolio optimization for diversification, value at risk, etc..


Each section of code is designed to stand alone, complete with references to data and required packages. 

Please contact me if you find typos or if you have suggestions for new items to add to the glossary.  <aguilar-mike@outlook.com> | <https://www.linkedin.com/in/mike-aguilar-econ/> 

A special thanks to Ziming Huang <https://www.linkedin.com/in/ziming-huang/> for tremendous contributions to this document.  

# Explore
```{r child = 'Ch1-Explore/Ch1.Rmd'}
```



# Explain
```{r child = 'Ch2-Explain/Ch2.Rmd'}
```



# Forecast
```{r child = 'Ch3-Predict/Ch3.Rmd'}
```



# Protect
```{r child = 'Ch4-Protect/Ch4.Rmd'}
```
